### 2018-02-13 thermoelectricity/paper.tex
added first table

>>>>

	\paperfig{TableOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_{in}}\papertableuheadersymbole{V_{in}}\\
	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{1.541}{.01}\papertableuval{3.197}{.005}\\\paperiline
\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{1.386}{.01}\papertableuval{2.884}{.004}\\\paperiline
\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{1.197}{.01}\papertableuval{2.488}{.004}\\\paperiline
\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{0.982}{.01}\papertableuval{2.044}{.004}\\\paperiline
\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{0.693}{.008}\papertableuval{1.441}{.004}\\\paperiline
\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.006}{.005}\papertableuval{0.014}{.003}\\\paperoline
\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
